---
title: "frETH Simulations"
author: "CharlieDAO"
date: "12/30/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warn = FALSE, message = FALSE)
```

## Intro 

Deep Freeze provides intrinsic yield for long term holdings of blockchain 
native assets (e.g., ETH on Ethereum). This report details a simple simulation
of random vaults, deposits, time-periods of lock, and patience profiles of 
vault owners to understand potential reactions to the Deep Freeze tokenomics
model as described in Tokenized Patience - the Deep Freeze Intrinsic Yield 
white paper. Please see this paper for more on the theory of intrinsic yield
and tokenized patience.

## Plan 

There are `n` vaults each owned by a single individual for simplicity's sake.
Each vault has: 

    * a random amount of ETH deposited
    * a random year of deposit (2021 - 2025)
    * a random amount of time (1 - 5 years) that deposit is locked
    * the resulting amount of frozen ETh "frETH" minted via that lock
    * the amount of time that must pass (in years) for a vault to be "breakeven" (67% of lock time)
    * Cost breakdrowns (in frETH) for withdrawing from the freezer at 5 points in time: 
        - Immediate withdrawal (i.e. mint amount + 20% frETH penalty)
        - Early withdrawal (mint amount + 10% frETH penalty)
        - Breakeven (mint amount, no frETH penalty)
        - Mostly through lock time (50% of mint amount, i.e. a frETH profit)
        - Completed lock time (can withdraw without returning any mint amount, i.e. 100% frETH profit)
        
Each vault is assigned a random `profile` indicating a *patience profile* of the vault owner.
This profile matches the cost breakdown as described above (i.e. a `completer` withdraws
without any frETH rebate or penalty, while `mostly` requires a 50% rebate but no penalty, etc.).
    
5 different market profiles probabilities are simulated to understand potential frETH
supply amounts and fees paid to FRZ token stakers (again, see the white paper for more 
details on tokenomics): 

1. Market has Extreme impatience
2. Moderate impatience
3. Balanced 
4. Moderate patience
5. Extreme patience 

Each market profile is analyzed as an evolving time series where each of 
5 time periods of analysis (2022 - 2026) are reviewed. 

I.e., in 2022, analysis is done on vaults with a deposit of 2021 OR 2022, 
and depending on the vault patience profile and deposit time, the vaults
are live (vault owner has an ongoing deposit) or completed (vault owner 
either withdrew early based on their patience profile or completed their 
deposit after the deposit time specified).  

For each time period market profile, the following metrics are assessed: 

    1. Total ETH deposited
    2. Total frETH minted (ETH deposits * ETH time locks)
    3. Total frETH penalties paid
    4. Total frETH penalties burned (50% of penalties paid) = frETH penalties paid to stakers
    5. Outstanding frETH supply (minted - burned)
    6. Outstanding frETH supply (minted - 50% penalties paid) per ETH deposited
    7. Outstanding frETH supply / frETH minted
    8. ETH paid to FRZ stakers (0.5% of ETH deposited by all except those who complete their lock)
    
Analysis will focus on the flows of frETH mints & burns and their overall effect on the frETH supply.


## Vault Simulation 

Given 100,000 vaults of (truncated) normally distributed amounts of 1+ eth deposited 
for (truncated) normally distributed times of 1+ years, we see the following 
distributions.

```{r}
library(ggplot2)
set.seed(4) # reproducible randomness
n = 100000 # 100000 vaults
initial_penalty = 0.2
frETH_penalty_burn_rate = 0.5 

random_id <- function(){
  # generate 1 of 250M+ potential random IDs
  paste0(
    sample(x = c(LETTERS, 0:9),size = 10, replace = TRUE),
    collapse = "")
}

vaults <- data.frame(
  vault_id = replicate(n = n, random_id()),
  deposit = abs(floor(rnorm(n)*10)) + 1,
  deposit_year = sample(x = 2021:2025, size = n, replace = TRUE),
  time = abs(floor(rnorm(n))) + 1
)

make_density <- function(x, bw = 1, xlab = "Amount of ETH Deposited"){ 
  ggplot(data = data.frame(val = x), aes(x = x)) +
    geom_histogram(aes(y=..density..), binwidth = bw, 
                   alpha=0.5, 
                position="identity") + 
    geom_density() + 
    theme_classic() +
    xlab(label = xlab)
  }

make_density(vaults$deposit)

make_density(vaults$time, bw = 0.1, xlab = "Amount of Time Locked")

```

Locking ETH mints frETH as a function of `deposit` amount * `time` locked and 
has a similar distribution:

```{r}
vaults$breakeven_time <- vaults$time * .67

vaults$mint <- vaults$deposit*vaults$time
vaults$initial_cost <- vaults$mint* ( 1 + initial_penalty) 
vaults$early_cost <- vaults$mint* ( 1 + 0.5*initial_penalty)
vaults$mostly_cost <- vaults$mint*0.5

make_density(vaults$mint, bw = 5, xlab = "Amount of frETH minted by Vault")

```

A sneak peek of the resulting vault table with cost breakdowns is provided here:

```{r}
knitr::kable(head(vaults, 10))
```

## Patience Profiles

```{r}

# workhouse functions 
profile <- c("early","breakeven","mostly","completer")
vault_check <- function(vault_row){
  
  minted = vault_row$mint
  
 cost_to_withdraw <- switch(vault_row$profile, 
        early = vault_row$early_cost,
        breakeven = vault_row$mint,
        mostly = vault_row$mostly_cost,
        completer = 0
        )
  
 marginal_supply = minted - cost_to_withdraw 
 
 return(marginal_supply)
}
get_supply_effect <- function(vaults){ 
  
supply_effect <- rep(0,n)
for( i in 1:nrow(vaults) ){ 
  supply_effect[i] <- vault_check(vaults[i, ])
}
vaults$supply_effect <- supply_effect 

return(vaults)  
}
get_metrics <- function(vaults){ 
  #'  1. Total ETH deposited (any amount of time)
  #'  2. Total frETH minted (ETH deposits * ETH time locks)
  #'  3. Total frETH penalties paid
  #'  4. Total frETH penalties burned 
  #'  5. Outstanding frETH supply (minted - burned)
  #'  6. Outstanding frETH supply (minted - burned) per ETH deposited
  #'  7. Outstanding frETH supply / frETH minted
  #'  8. ETH paid to FRZ stakers (0.5% of ETH deposited by all except those who complete their lock)
    
  tbl <- data.frame(
    "ETH Deposited" = sum(vaults$deposit), 
    "frETH Minted" = sum(vaults$mint), 
    "frETH Penalties Paid" = -sum( vaults[vaults$supply_effect < 0, "supply_effect"] ),
    "frETH Penalties Burned" = {
      -frETH_penalty_burn_rate * sum( vaults[vaults$supply_effect < 0, "supply_effect"] )
      },
    "frETH Supply" = { 
      # mint - burn // here mint + 1/2 burn (which is already negative)
      sum(vaults$mint) + 
        frETH_penalty_burn_rate * sum( vaults[vaults$supply_effect < 0, "supply_effect"] )
      },
    "frETH supply per ETH deposited" = { 
      (sum(vaults$mint) + 
         frETH_penalty_burn_rate*sum( vaults[vaults$supply_effect < 0, "supply_effect"] )) / 
        sum(vaults$deposit)
      },
    "frETH supply per frETH Minted" = { 
      (sum(vaults$mint) + frETH_penalty_burn_rate * sum( vaults[vaults$supply_effect < 0, "supply_effect"] )) / 
        sum(vaults$mint)
      },
    "ETH Fees Paid" = 0.0025 * sum(vaults[vaults$profile!= "completer", "deposit"]),
    check.names = FALSE, 
    row.names = NULL
  )

  return( tbl )
  }

```

### Extreme Impatience 

Extreme impatience is characterized by: 

70% of vaults withdrawing prior to their breakeven date ("early")
15% of vaults withdrawing exactly at breakeven ("breakeven")
10% of vaults withdrawing near completion ("mostly")
5% of vaults withdrawing upon completion

The resulting metrics are provided here:

```{r}
# reproducibility set above - run entire markdown at once 

extreme_impatience <- vaults
extreme_impatience$profile <- sample(x = profile, 
                                  size = n,
                                  replace = TRUE,
                                  prob = c(0.70,
                                           0.15,
                                           0.10,
                                           0.05))
extreme_impatience <- get_supply_effect(extreme_impatience)

knitr::kable(get_metrics(extreme_impatience))

```

